### 2019-03-19 _publications/jors/paper.tex
Update for tkphd review

\section{Title}
\par\bigskip
PFHub: The Phase-Field Community Hub\\[\baselineskip]
\url{https://pages.nist.gov/pfhub}

@@

Scientific research communities often require an online portal to
summarize a shared challenge, collect attempts at a solution, and
present a quantitative comparison of past attempts in a compelling
way. An exemplar of such a portal is $\mu$MAG~\cite{mumag}. The
reusable PFHub framework leverages existing online services to build a
static portal website that is considerably easier to deploy and
maintain without sacrificing content or scope. The first deployment of
the PFHub framework supports phase-field practitioners and code
developers participating in an effort to improve quality assurance for
phase-field codes.

@@

The phase-field method (PFM) describes material interfaces at the
mesoscopic scale between atomic scale models and macroscale models.
The PFM is well established and there are an assortment of code
frameworks (\emph{e.g.}, Moose~\cite{moose},
PRISMS-PF~\cite{prisms-pf}, FiPy~\cite{fipy}, MMSP~\cite{mmsp})
available for solving the wide variety of phenomena associated with
phase-field (\emph{e.g.}, dendritic growth, spinodal decomposition,
grain growth). However, phase-field research groups often develop
codes in isolation and do not publish the code bases or do not support
or distribute the code bases to the wider community. PFHub is a
community effort spearheaded by the Center for Hierarchical Materials
Design at Northwestern University and the National Institute of
Standards and Technology to support the development of phase-field
codes. The goal of PFHub is to improve cross-collaboration between
phase-field code developers and practitioners by providing a
standardized set of benchmark problems~\cite{bm1, bm2} along with a
web framework for uploading and comparing benchmark results from
different codes.

@@

\begin{itemize}
  \item The users are first required to archive simulation outputs at
    an archival resource (\emph{e.g.}, Figshare) configured with
    permissive cross-origin resource sharing (CORS).
  \item The metadata summarizing each simulation is entered into a
    form on the website, including relevant details such as memory
    usage, run time and links to the data archived in the first step.
  \item Upon submission, the Staticman app~\cite{staticman} submits
    the entered metadata as a GitHub pull request to the PFHub GitHub
    repository.  The metadata is stored in a YAML file with a unique
    path in the repository.
  \item Travis CI~\cite{travis} performs linting on the submission and
    then launches a new version of the website using
    Surge~\cite{surge}. The PFHub admins can then examine the new
    submission and further changes can be made if necessary.
  \item Once review has been completed to the satisfaction of both the
    uploading scientist and the website maintainers, the pull request
    is merged and served to the World Wide Web using a hosting service
    compatible with GitHub Pages.
\end{itemize}

A combination of Jekyll templates and Coffeescript are used to access
and download the data links in the submitted YAML files and then
display the data in interactive figures on the website. The
combination of a central repository on GitHub for website source code
and metadata with distributed data records on third-party archives
avoids the complexity and administrative overhead of maintaining a
live database and associated backend app. The PFHub infrastructure
provides a template for other small scientific communities to host
custom content and integrate data from members of their community.

\begin{figure}
  \includegraphics[width=4in]{pfhub_website.png}
  \caption{Schematic overview of the PFHub framework for building
    scientific research portals, simply.}
  \centering
  \label{fig:pfhub_website}
\end{figure}

@@

PFHub is currently built and tested using the programming language and
versions outlined in Table~\ref{tab:versions}.

@@

The website infrastructure can be forked and deployed with minimum
effort including the upload mechanism using Staticman. However,
customizing the website for a particular scientific community would
require considerable effort. The following steps are the more
challenging aspects of deploying the framework for a new community.

\begin{itemize}
  \item Edit or upload new Jupyter Notebooks with benchmark or data
    requirement descriptions.
  \item Edit the \texttt{benchmarks.yaml} file to reflect the new
    upload requirements and describe the figures that need to be
    generated on the upload comparison pages.
  \item Edit the \texttt{\_config.yml} file to update links and text
    related to the configuration for all aspects of the website.
  \item Update Markdown files to reflect the new content and mission
    of the scientific community.
  \item Remove data and files that are not required by the new
    community.
\end{itemize}

@@

%% \section*{References}

@@

%% \textcolor{blue}{Please enter references in the Harvard style and include a DOI where available, citing them in the text with a number in square brackets, e.g. \\ }

%% \textcolor{blue}{[1] Piwowar, H A 2011 Who Shares? Who Doesn't? Factors Associated with Openly Archiving Raw Research Data. PLoS ONE 6(7): e18657. DOI: \\ http://dx.doi.org/10.1371/journal.pone.0018657.}

\vspace{2cm}

\rule{\textwidth}{1pt}

{ \bf Copyright Notice} \\
Authors who publish with this journal agree to the following terms: \\

Authors retain copyright and grant the journal right of first publication with the work simultaneously licensed under a  \href{http://creativecommons.org/licenses/by/3.0/}{Creative Commons Attribution License} that allows others to share the work with an acknowledgement of the work's authorship and initial publication in this journal. \\

Authors are able to enter into separate, additional contractual arrangements for the non-exclusive distribution of the journal's published version of the work (e.g., post it to an institutional repository or publish it in a book), with an acknowledgement of its initial publication in this journal. \\

By submitting this paper you agree to the terms of this Copyright Notice, which will apply to this submission if and when it is published by this journal.

>>>>

\section*{Title}
\par\bigskip
PFHub: The Phase-Field Community Hub\\[\baselineskip]
\url{https://pages.nist.gov/pfhub}

@@

Scientific research communities often require an online portal to
summarize a shared challenge, collect attempts at a solution, and
present a quantitative comparison of past attempts in a compelling
way. An exemplar of such a portal is
$\mu$MAG~\cite{mumag}~\footnote{Certain commercial equipment,
  instruments, or materials (or suppliers, or software, ...) are
  identified in this paper to foster understanding. Such
  identification does not imply recommendation or endorsement by the
  National Institute of Standards and Technology, nor does it imply
  that the materials or equipment identified are necessarily the best
  available for the purpose.\label{disclaimer}}. The reusable PFHub
framework leverages existing online services to build a static portal
website that is considerably easier to deploy and maintain without
sacrificing content or scope. The first deployment of the PFHub
framework supports phase-field practitioners and code developers
participating in an effort to improve quality assurance for
phase-field codes.

@@

The phase-field method (PFM) describes material interfaces at the
mesoscopic scale between atomic scale models and macroscale models.
The PFM is well established and there are an assortment of code
frameworks (\emph{e.g.}, Moose~\cite{moose},
PRISMS-PF~\cite{prisms-pf}, FiPy~\cite{fipy},
MMSP~\cite{mmsp}~\textsuperscript{\ref{disclaimer}}) available for
solving the wide variety of phenomena associated with phase-field
(\emph{e.g.}, dendritic growth, spinodal decomposition, grain
growth). However, phase-field research groups often develop codes in
isolation and do not publish the code bases or do not support or
distribute the code bases for the wider community. PFHub is a
community effort spearheaded by the Center for Hierarchical Materials
Design at Northwestern University and the National Institute of
Standards and Technology to support the development of phase field
codes. In particular, the PFHub effort focuses on improving
cross-collaboration between phase-field code developers and
practitioners by providing a standardized set of benchmark
problems~\cite{bm1, bm2} along with a web framework for uploading and
comparing benchmark results from different codes.

@@

\begin{itemize}
  \item The users are first required to upload simulation outputs to
    an archival resource (\emph{e.g.}, Figshare) configured with
    permissive cross-origin resource sharing (CORS).
  \item The metadata summarizing each simulation is entered into a
    form on the website, including relevant details such as memory
    usage, run time and links to the data archived in the first step.
  \item Upon submission, the Staticman app~\cite{staticman} submits
    the entered metadata as a GitHub pull request to the PFHub GitHub
    repository.  The metadata is stored in a YAML file with a unique
    path in the repository.
  \item Travis CI~\cite{travis} performs linting on the submission and
    then launches a temporary version of the proposed website using
    Surge~\cite{surge}. The PFHub admins can then examine the new
    submission and further changes can be made if necessary.
  \item Once review has been completed to the satisfaction of both the
    uploading scientist and the website maintainers, the pull request
    is merged and served to the World Wide Web using a hosting service
    compatible with GitHub Pages.
\end{itemize}

A combination of Jekyll templates and Coffeescript are used to access
and download the data links in the submitted YAML files and then
display the data in interactive figures on the website. The
combination of a central repository on GitHub for website source code
and metadata with distributed data records on third-party archives
avoids the complexity and administrative overhead of maintaining a
live database and associated back-end application. The PFHub
infrastructure provides a template for other small scientific
communities to host custom content and integrate data from members of
their community.

\begin{figure}
  \includegraphics[width=\textwidth]{pfhub_website.png}
  \caption{Schematic overview of the PFHub framework for building
    scientific research portals, simply.}
  \centering
  \label{fig:pfhub_website}
\end{figure}

@@

PFHub is currently built and tested using the programming languages
and versions outlined in Table~\ref{tab:versions}.

@@

The website infrastructure can be cloned as a Git repository or
downloaded as a ZIP archive and deployed with minimum effort. The
mechanism for uploading data using Staticman can be easily configured
for a new repository location. However, customizing the content of the
website for a particular scientific community would require
considerable effort. The following steps are the more challenging
aspects of deploying the framework for a new community.

\begin{itemize}
  \item Upload new benchmark defintions in a format that Jekyll can
    parse, \emph{e.g.}, Jupyter Notebook, Markdown or HTML.
  \item Edit the \texttt{benchmarks.yaml} file to reflect the new
    upload requirements and describe the figures that need to be
    generated on the upload comparison pages.
  \item Edit the \texttt{\_config.yml} file to update links and text
    related to the configuration for all aspects of the website.
  \item Update Markdown files to reflect the new content and mission
    of the scientific community.
  \item Remove data and files that are not required by the new
    community.
\end{itemize}

@@

@@
